### 2019-06-05 manuscript.tex
Update manuscript.tex

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{AdnrLesc16, UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}.

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}

@@

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in 
 main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Our main interest in this project is to study how norms associate with behavioural intention.  We focus on how women will likely cut their daughters or not based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g. women’s own FGC status).  Therefore, our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.  In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status and beliefs of FGC benefits.  Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, gender awareness (see — for questions of gender awareness proxy) and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}

@@

Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.  Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.  In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.}

@@

- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
 \cit{Hayf05}  Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
\cite{KandNwak09,VanMeek15} proposing various factors impacting FGC practices, such as women's education

\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
% religion:  \cite{HayfTrin11, KarmKand11}

— by nations and laws in those nations—

@@

— Suggestions —
- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)

@@

\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),

--- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.

@@

%\cfcmt{Bicchieri's norm theory \cite{Bicc06}:
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do

>>>>

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{AdnrLesc16, UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01} and Tostan (https://www.tostan.org/programs/community-empowerment-program/).

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. (and BoylMcMo02)

Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and analyzed \cite{DuncWand11, EffeVogt15, Hayf05,,, Youn02, }.  For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}

@@

% norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in 
 main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples.  We included all the women with daughters who had not genital cutting because those women presented an attitude of whether to genitally cut their daughter and represented part of the community norm in the first two models.   As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Our main interest in this project is to study how norms associate with behavioural intention.  We focus on whether women will likely genitally cut their daughters based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g. women’s own FGC status).  Therefore, our main response variables were woman's behavioural intention to cut their daughters genital in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.  In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status and beliefs of FGC benefits.  Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, gender awareness (see — for questions of gender awareness proxy) and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
\cfcmt{Do we explain conveyance of uncertainty and data sampling?}

@@

Our findings suggest that the likelihood of whether a mother will have their daughters genital cut is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.  Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benits was the strongest predictor of mother’ intention of cutting daughters.
\cite{ShelWand11}:“alternative convention/peer convention.  Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}.

- descriptive norm:  what others do. In our case, is it fgc prevalence in a community?

 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.  In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.}

@@

- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
 \cit{Hayf05 SipsChen12}  Wealth.  \cite{Hayf05}: Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status

% age\cite{PashPonn16, SipsChen12}, \cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media

\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
\cite{Hayf05, PashPonn16} (more)

% education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.

% religion:  \cite{HayfTrin11, KarmKand11}

% media:  \cite{DalaLawo10}

% Refer the findings to \cite{BiccMari15} on fgc dynamics/freedom/fgc prevalence trend/econcomic development etc in the 4 nations. (e.g., table 8)
— by nations and laws in those nations—

@@

— Suggestions —

Changing social norm is a key step to changing behaviour  \cie{Bicc10}.  Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.  An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour. (using Tostan as an example) (also see \cite{Youn15}.  Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).

- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)
- a bottom-up intervention aimed at changing social expectation \cite{BiccMari15}
- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework \cite{CislHeis18a, CislHeis18b, McCh15}.  Empowering local community and opinion leaders in implementing “organized diffusion” \cite{MackLeJe08}has proven cost-effective \cite{CislDenn19}. (and Boston?)

@@

%  while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),

--- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}  Attitude is “personal evaluation of a behaviour” \cite{Ajze91}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.

@@

%\cfcmt{Bicchieri's norm theory \cite{Bicc06, BiccMari15}:
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do/Personal normative beliefs are individual’s beliefs about the value of a practice. 
empirical expectation:  What the responder believes others do/What others do/second-order beliefs about the normative beliefs of other people (Bicchieri, 2006) 
normative expectation: What the responder believes others think she should do/what other people believe one should do
“individuals may actively dislike the behavior imposed by the norm, but still obey it if their social expectations point in that direction. “
